Relaxed Weak Accelerated Proximal Gradient Method: a Unified Framework for Nesterov's Accelerations

### 2025-10-28 Notebook LaTEX/R-WAPG/presentation-short.tex
>w<, all fixes

                How much can we relax the choice of the sequence $\theta_k$ and still get an upper bound for the convergence rate? 

@@

                \item It relaxes the assumption of the momentum sequence parameter while still retaining an upper bound on the optimality gap. 

@@

                    {\rho_k\alpha_k^2 + \alpha_k}(x_{k + 1} - x_k). 

@@

                    \STATE{$\theta_{k + 1} := \alpha_k(1 - \alpha_k)/(\alpha_k^2 + \alpha_{k + 1})$;}

@@

@@

                \item The smallest value of $F(x_k)$, for all algorithms, over all tries are taken as an estimate of $F^+$. 

@@

        \begin{frame}{Results plotted}
            With $A\in \RR^{N\times N}$ fixed, for each $x_0 \sim \mathcal N(I, \mathbf 0)$ realized, 30 experiments are preformed and the medium, minimum and maximum of $\delta_k$ are recorded for M-FISTA, Free R-WAPG, and V-FISTA. 

>>>>

                How much can we relax the choice of the sequence $\theta_k$ and retain an upper bound for the convergence rate? 

@@

                \item It relaxes the assumption of the momentum sequence parameter while retaining an upper bound on the optimality gap. 

@@

                    {\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 

@@

                    \STATE{$\theta_{k + 1} := \alpha_{k + 1}(\alpha_k^{-1} - 1)$;}

@@

                \item $\lambda = 0.1$. 

@@

                \item Let $F_{\min}$ be the smallest value of $F(x_k)$, for all algorithms, over all trials, we estimate $F^+$ by $F^+ = F_{\min}*(1 - 2^{53})$. 

@@

        \begin{frame}{LASSO Results plotted}
            With $A\in \RR^{N\times N}$ fixed, for each $x_0 \sim \mathcal N(I, \mathbf 0)$ realized, 20 experiments are preformed and the medium, minimum and maximum of $\delta_k$ are recorded for M-FISTA, Free R-WAPG, and V-FISTA. 
